---
title: "Exporation"
output: html_document
date: "2022-09-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(Seurat)
```


# Load Data

```{r}
## HTO classification
hto_class <- read_csv(here("data", "HTO_classifications_hume_dat_12_2021.csv"))

## Seurat Object 
integrated_hume <- readRDS(here("data", "integrated_hume_12_2021.Rds"))

#3 Library IDS from C Loupe 
cloupe = read_csv(here("data", "LibraryID.csv"))

```
## Questions about Library IDS from C Loupe

* I exported IDS from c loupe from the hume_results_12_2021 folder and the C Loupe Bar Codes and the hto_class bar codes only have 29333 (out of 93296 possible) matches. This tells me that the appendixes used on the barcodes from these two data sets DO NOT match. 

```{r}
sum(sort(hto_class$Barcode) %in% sort(cloupe$Barcode))
```



## Following code from when cloupe and seurat cell names are not the same 

** This merges cloupe and Seurat

```{r}
# Start with the cloupe cell names. 
# Here we pull off the appendix to get the original barcode for the cell
x <- strsplit(as.character(cloupe$Barcode), split='-')
cloupe$orig_barcode <- unlist(lapply(x, function(z) z[[1]]))
cloupe$barcode_append <-unlist(lapply(x, function(z) z[[2]]))

md <- integrated_hume@meta.data
md$rowname <- rownames(md)
md$order <- seq(1, nrow(md))

# Now we do the same thing with the Seurat cell names to get the original barcode
x <- strsplit(as.character(md$rowname), split='_')
md$orig_barcode <- unlist(lapply(x, function(z) z[[1]]))
x <- strsplit(as.character(md$orig_barcode), split='-')
md$orig_barcode <- unlist(lapply(x, function(z) z[[1]]))

# Check that all barcodes in seurat are present in the cloupe file
table(md$orig_barcode %in% cloupe$orig_barcode)

# I had to create a libraryID variable that matched the sample names in cloupe 
md$LibraryID <- gsub("dat_","",as.character(md$orig.ident))
md = md %>% mutate(LibraryID = case_when(
  LibraryID == "471_NS" ~ "471_NS_FR",
  TRUE ~ LibraryID
))

table(md$LibraryID %in% cloupe$LibraryID)

# For each sample, check that all barcodes in seurat appear in cloupe
for(i in unique(md$LibraryID)){
  print(table(md[md$LibraryID==i,]$orig_barcode %in% cloupe[cloupe$LibraryID==i,]$orig_barcode))
}

# Merge the files together by library ID and original barcode
md <- merge(md, cloupe[,c("Barcode", "LibraryID", "orig_barcode")])

rownames(md) <- md$rowname
md <- md[order(md$order),]

integrated_hume@meta.data <- md

```



## Merge the Meta Data with HTO class 

* The Barcode from hto class and from the cloupe (now merged into md) do not match. Believe I need to use the row name bar code from md

```{r}
# Get the original barcode and the appendix for each cell
x <-strsplit(hto_class$Barcode, '-')
hto_class$barcode_append <- unlist(lapply(x, function(x) x[2]))

sample_num <- data.frame(barcode_append = seq(1,8,1), 
                         orig.ident = c("Nov15_one_479_NS_Merge", "Nov15_two_480_Merge", "471_NS", 
                                        "Nov16_two_477_NS_Merge", "Nov17_two_470_S_Merge", "Nov18_one_461_NS_Merge", 
                                        "Nov18_two_465_S_Merge", "Nov22_two_462_S_Merge"))

# Add sample name info to the HTO data
hto_class <- merge(hto_class, sample_num)
hto_class$orig_barcode <- unlist(lapply(x, function(x) x[1]))

integrated_hume@meta.data$tissue <- NA


for (i in unique(sample_num$orig.ident)){
  for(j in unique(hto_class$HTO_classification)){
    barcodes <- hto_class[hto_class$orig.ident==i & hto_class$HTO_classification==j,]$orig_barcode
    integrated_hume@meta.data$tissue[integrated_hume@meta.data$LibraryID==i & integrated_hume@meta.data$orig_barcode %in% barcodes] <- j
  }}


saveRDS(integrated_hume, here('data','integrated_all_samples.RDS'))

```



# Questions

* Are 471_NS_FR (cloupe library id) and dat_471_NS (seurat id) the same sample? 
  + currently assuming yes 